module2_eco_pol_factors

### 2022-03-10 moduletwoanalysis.Rmd
distributiion graphs for Kahan scale

---
title: "module2_eco_pol_factors"
output:
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    keep_md: true
    theme: paper
    df_print: paged
---

@@

#trying to work with likert packages here

likertstack <- module2%>%
  filter(!row_number() %in% c(1,2)) %>% 
  select(starts_with("RISKY"))%>%
  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
  select(-Risky) %>% 
  group_by(Technology, Perceived_Risk) %>%
  summarise(n=n()) %>%
  pivot_wider(names_from = "Perceived_Risk", values_from = "n")

likert(Measure ~ ., data=likertstack, ylab=NULL,
       ReferenceZero=3, as.percent=TRUE,
       positive.order=TRUE, 
       main = list("Pereived risk from energy technologies in India",x=unit(.55, "npc")), 
       sub= list("Perceived risk",x=unit(.57, "npc")), 
       xlim=c(-40,-20,0,20,40,60,80,100),
       strip=FALSE, 
       par.strip.text=list(cex=.7))
```

@@

>>>>

---
title: "module2_eco_pol_factors"
output:
  word_document: default
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

@@

```
```{r}
 #median score for Kahan invidualism scale

codedmodule2 %>%
  select((starts_with(c("K_I", "K_S"))))%>%
  gather(key = "K_I", value = "score")%>%
  na.omit()%>%
  summarise(median = median(c(score)))

```
```{r}

# Kahan scale median score for Hierarchy scale
codedmodule2 %>%
  select((starts_with(c("K_H", "K_E"))))%>%
  gather(key = "K_H", value = "score")%>%
  na.omit()%>%
  summarise(median = median(c(score)))
```

```{r}
#calculating individualism score for each respondent

Kscalescores <- codedmodule2 %>%
  select(starts_with(c("Risky","K_I","K_S", "K_H", "K_E")))%>%
  rowwise()%>%
  na.omit()%>%
  mutate(Individualism_score = mean(c_across(K_IINTRFER:K_SPROTECT)))%>%
  mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
  select(!starts_with(c("K_I","K_S", "K_H", "K_E")))

Kscalescores

#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.

Kscalescores %>%
  ggplot(aes(Individualism_score, Hierarchy_score))+
  geom_point()+
  geom_hline(yintercept=2, colour="black", lwd=1)+
  geom_vline(xintercept=3, colour="black", lwd=1)

```{r}
# checking distribution of scores on Individualism scale

Kscalescores %>%
  ggplot(aes(x=Individualism_score, y = ..count..), fill = "lightgray")+
  geom_density()

```{r}
# checking distribution of scores on Hierarchy scale 
Kscalescores %>%
  ggplot(aes(x=Hierarchy_score, y = ..count..), fill = "lightgray")+
  geom_density()
```
